---
title: "Master's Project"
author: "Ignacio Leiva"
institute: "Charite"
date: "October"
output:
  xaringan::moon_reader:
    css: 
      - default
      - css/thesis.css
      - css/thesis-fonts.css
    lib_dir: libs
    seal: false
    nature:
      highlightStyle: googlecode
      highlightLines: true
      highlightLanguage: ["r"]
      countIncrementalSlides: false
      ratio: "16:9"
    includes:
      after_body: [css/logo.html]
---


```{r setup, include = FALSE}
library(knitr)
library(tidyverse)
library(tufte)
library(DT)
# set default options
opts_chunk$set(echo = FALSE,
               fig.width = 7.252,
               fig.height = 4,
               dpi = 300)

```

class: title-slide, center, middle

# `r rmarkdown::metadata$title`
<br>
### .black[`r rmarkdown::metadata$author`]

---
class: inverse, middle, center

# "Relationship between socioeconomic status, adherence to antiretroviral therapy and HIV viral suppression"
<br>
<br>
<br>
<br>

.pull-left[
**Dr. Claudia Cortes**

Fundación Arrirán,Chile
]
.pull-right[
**Dr. Barbara Gunsenheimer-Bartmeyer**

Robert Koch Institute

]


---
class: middle

#.charite[Research question]


.my-one-page-font.center[How does **employment status** affect **antiretroviral treatment adherence** and **HIV viral suppression** among patients in a healthcare centre in Chile?]


---
# Methodology

## .charite[Data source]
- **Project**: An AI-based computer platform to characterize and identify the level of adherence to treatment among HIV+ people
- Cross-sectional study (Feb-Nov 2021)
  - Self-administer questionnaire
  - Clinical data from pharmacy

---
# Variables
.pull-left[
### .charite[Outcomes/exposure]
- VL at $\leq$ 50 copies/mL and $\leq$ 200 copies/mL
- Proportion of days covered (PDC): Adherence proxy
- Employment status (four or two levels)
   ]
   
.pull-right[
### .charite[Covariates]
- Gender & age (years)
- Level of education (binary based on years)
- Social priority (Metropolitan zone)
- Type of ARV (STR & family)
- Migratory background (binary)
- Commodities (binary)
- Health insurance (strata from A to D)
- Time on ARV (years)
- Homelessness (binary)
- Addictions (address with 1 question)
   ]
---
# Operazionalization
## Proportion of days covered (PDC), AdhereR

```{r}
library(AdhereR)
pdc <- readxl::read_excel("PDC.xlsx", sheet = 1)

PDC12m <- CMA7(data= pdc, # we're estimating CMA8 now!
             ID.colname="id",
             event.date.colname="date",
             event.duration.colname="days",
             event.daily.dose.colname="perday",
             medication.class.colname="drug",
             carry.only.for.same.medication=TRUE,
             consider.dosage.change=FALSE,
             followup.window.start=0, 
            followup.window.start.unit= "days",
            followup.window.duration= 180,
            observation.window.start= 0, #TO DETERMINE WHEN START, BUT LOOKIN THE NUMBER
            observation.window.start.unit="days",
             observation.window.duration=180,
             date.format= "%m/%d/%Y")

plot(PDC12m, patients.to.plot=c("1"), show.legend= TRUE)
```
---
# Data Analysis 

- Variable selection using Directed Acyclic Graph (DAG) on Dagitty
- Multivariable logistic regression

---
class: inverse, middle, center
# Some results so far

---
## Variable selection 
### Minimal sufficient adjustment sets the total effect of Employment status on Viral load and PDC. [See](http://dagitty.net/dags.html?id=UDvDOn)
.pull-left[
- Age (a)
- Gender (g)
- Education Level (e)
- Addiction (ad)
       ]
.pull-right[
- Homelessness (h)
- Commodities (c)
- Migratory background (m)<sup>1</sup>
- Social priority (s)
    ]



###Regression model


> $$\scriptsize \log_e (odds[detectable])=\beta_0 + \beta_{EmpS}\times EmpS + \beta_{a}\times a + \beta_{g}\times g + \beta_{c}\times c + \beta_{e}\times e + \beta_{h}\times h + \beta_{s}\times s + \beta_{m}\times m + s + \beta_{ad}\times ad$$

.center[.footnote[<sup>1</sup> check [Daggity](http://dagitty.net)]]
---
class: 
## .charite[Domographic]


```{css, echo = F}
table {
  font-size: 16px;    
  line-height: 0.7em;
}


```


```{r}
covariates <- readRDS("/Users/igna/Documents/R projects/thesis_presentation/documents/covariates.RData")
covariates$variable[covariates$variable == "sex"] <- "Gender"
covariates$variable[covariates$variable == "age"] <- "Age"

covariates$variable[covariates$variable == "n_year_education"] <- "Education (years)"
covariates$variable[covariates$variable == "Did patient has chornic disease (no = 1, yes = 0 "] <- "Comorbidities"
covariates$variable[covariates$variable == "social_priority"] <- "Social priority"


DT::datatable(covariates, class = "hover", rownames = FALSE, options = list(dom = 'tBp', pageLength = 14,#, width = 800,
              #caption = 'Table 1: Demographic Distribution.'
              initComplete = JS(
        "function(settings, json) {",
        "$(this.api().table().header()).css({'background-color': '#f7ebec', 'color': 'black'});",
        "}")))%>% 
  formatStyle(
    1,
    target = "row",
    fontWeight = styleEqual(c("Gender","Age","Education (years)", "Comorbidities","migrant", "addiction","Social priority"), "bold"),
    `font-size`="16px"
  )%>% 
 formatStyle(
    2,
    target = "row",
    fontWeight = styleEqual("(N=748)", "bold"),
    `font-size`="16px"
  )

```

---
## .charite[Outcomes]
```{r}
outcome <- readRDS("/Users/igna/Documents/R projects/thesis_presentation/documents/outcome.RData")

outcome$variable[outcome$variable == "Adherence status (adh = 0, non_ad = 1"] <- "PDC (95%)"
outcome$variable[outcome$variable == "adherence levels"] <- "PDC levels"

DT::datatable(outcome, class = "hover", rownames = FALSE, options = list(dom = 'tBp', dom = 'tip', pageLength = 14, info = FALSE, autoWidth = FALSE, #,caption = 'Table 2: Outcome distribution.'
              initComplete = JS(
        "function(settings, json) {",
        "$(this.api().table().header()).css({'background-color': '#f7ebec', 'color': 'black'});",
        "}"))) %>% 
  formatStyle(
    1,
    target = "row",
    fontWeight = styleEqual(c("Viral load status (50 cp)","Viral load status (200 cp)","PDC (95%)", "PDC levels"), "bold"),
    `font-size`="16px"
  )%>% 
 formatStyle(
    2,
    target = "row",
    fontWeight = styleEqual("(N=748)", "bold"),
    `font-size`="16px"
  )

```

---
## .charite[Exposures]

```{r}

exposure <- readRDS("/Users/igna/Documents/R projects/thesis_presentation/documents/exposure.RData")

exposure$variable[exposure$variable == "Employment Status"] <- "Employment Status (4 Levels)"
exposure$variable[exposure$variable == "empl_status_3_factor"] <- "Employment Status (2 Levels)"

#widgetframe::frameWidget(demo)

DT::datatable(exposure, class = "hover", rownames = FALSE, options = list(dom = 'tBp', pageLength = 16,
              #caption = 'Table 3: Exposure distribution.'
              initComplete = JS(
        "function(settings, json) {",
        "$(this.api().table().header()).css({'background-color': '#f7ebec', 'color': 'black'});",
        "}")))%>% 
 formatStyle(
    1,
    target = "row",
    fontWeight = styleEqual(c("Employment Status (4 Levels)","Employment Status (2 Levels)"), "bold"),
    `font-size`="16px"
  )%>% 
 formatStyle(
    2,
    target = "row",
    fontWeight = styleEqual("(N=748)", "bold"),
    `font-size`="16px"
  )


#demo %>% 
 # DT::datatable(class = "compact", rownames = TRUE, extensions = "Buttons",
             #   options = list(dom = 'tBp', buttons = c("csv","excel"), 
                              # pageLength = 15))
```
---
## Odds Ratios VL ~ Employment Status
```{r}

#ORVL <- readxl::read_excel("/Users/igna/Documents/R projects/thesis_presentation/documents/RegressionVL.xlsx", sheet = 1)



ORVL <- readRDS("/Users/igna/Documents/R projects/thesis_presentation/documents/RegressionVL.RData")
#table1::table1(~Variable + OR  | group, data = ORVL)
row.names(ORVL)[3]<- "Retired"
row.names(ORVL)[4] <- "Student"
row.names(ORVL)[5] <- "Unemployed"
row.names(ORVL)[7] <- "Employed."
row.names(ORVL)[8] <- "Unemployed."
row.names(ORVL)[9] <- "Age"
row.names(ORVL)[12]<- "Transgender"
row.names(ORVL)[13] <- "Women"
row.names(ORVL)[16] <- "Yes"
row.names(ORVL)[19] <- ">12"
row.names(ORVL)[21] <- "No."
row.names(ORVL)[22] <- "Yes."
#ORVL$CI.97.5.[[3]] <- "inf" # change a value by position, third position in vector CI.97.5
names(ORVL)[2] <- "CI.2.5"
names(ORVL)[3] <- "CI.97.5"
names(ORVL)[6] <- "CI.2.5"
names(ORVL)[7] <- "CI.97.5."
ORVL$CI.97.5.[[3]] <- "inf" # change a value by position, third position in vector CI.97.5
#names(ORVL)[7] <- "CI.2.5."
#names(ORVL)[8] <- "CI.97.5."
#names(ORVL)[9] <- "p.value."

#ORVL <- tibble::rownames_to_column(ORVL, "Variable")
ORVL$N<- "PRUEBA"
ORVL$L<- "PRUEBA"
ORVL$M<- "PRUEBA"
#DT::datatable(ORVL, class = "display", rownames = FALSE, options = list(dom = 'tBp', buttons = c("csv","excel"), pageLength = 16))
```


```{r, echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
# a custom table container
sketch = htmltools::withTags(table(
  class = 'hover',
  thead(
    tr(
      th(rowspan = 2, 'Variable'),
      th(colspan = 4, 'Viral Load 50 cp'),
      th(colspan = 4, 'Viral Load 200 cp')
    ),
    tr(
      #lapply(names(ORVL)[-1], th)
      lapply(rep(c('OR', 'CI.2.5', 'CI.97.5', 'p-value'), 2), th)
    )
  )
))
#print(sketch)


```

```{r, echo=FALSE, message= FALSE, warning = FALSE}
datatable(ORVL, container = sketch, rownames = TRUE, class = "hover", options = list(dom = 'tBp', buttons = c("csv","excel"), pageLength = 13,
                                                                                 initComplete = JS(
        "function(settings, json) {",
        "$(this.api().table().header()).css({'background-color': '#f7ebec', 'color': 'black'});",
        "}")))%>% 
  formatStyle(
    0,
    target = "row",
    fontWeight = styleEqual(c("Employment Status (4L)","Employment Status (2L)", "Gender", "Social priority", "Education Level (years)", "Addictions"), "bold"),
    `font-size`="16px"
  )
```

---
## Odds Ratios PDC ~ Employment Status
```{r}

#ORVL <- readxl::read_excel("/Users/igna/Documents/R projects/thesis_presentation/documents/RegressionVL.xlsx", sheet = 1)



ORPDC <- readRDS("/Users/igna/Documents/R projects/thesis_presentation/documents/regressionsPDC.RData")
#table1::table1(~Variable + OR  | group, data = ORVL)
row.names(ORPDC)[3]<- "Retired"
row.names(ORPDC)[4] <- "Student"
row.names(ORPDC)[5] <- "Unemployed"
row.names(ORPDC)[7] <- "Employed."
row.names(ORPDC)[8] <- "Unemployed."
row.names(ORPDC)[9] <- "Age"
row.names(ORPDC)[12]<- "Transgender"
row.names(ORPDC)[13] <- "Women"
row.names(ORPDC)[16] <- "Yes"
row.names(ORPDC)[19] <- ">12"
row.names(ORPDC)[21] <- "No."
row.names(ORPDC)[22] <- "Yes."
#ORVL$CI.97.5.[[3]] <- "inf" # change a value by position, third position in vector CI.97.5
names(ORPDC)[2] <- "CI.2.5"
names(ORPDC)[3] <- "CI.97.5"
names(ORPDC)[4] <- "p-value"


```


```{r, echo=FALSE, message= FALSE, warning = FALSE}
datatable(ORPDC, rownames = TRUE, class = "hover", options = list(
  dom = 'tBp', pageLength = 13,
  initComplete = JS(
        "function(settings, json) {",
        "$(this.api().table().header()).css({'background-color': '#f7ebec', 'color': 'black'});",
        "}"))) %>% 
  formatStyle(
    0,
    target = "row",
    fontWeight = styleEqual(c("Employment Status (4L)","Employment Status (2L)", "Gender", "Social priority", "Education Level (years)", "Addictions"), "bold"),
    `font-size`="16px"
  )
```
